Data Analysis

### 2022-07-08 01.get_person_ids.Rmd
rearranging

```{r}
library(dplyr)
library(purrr)
library(bib2df)
library(tidyverse)
library(httr)

@@

library(scholar)
```

@@

```{r}
bibs <- bib2df("papers.bib")
```

@@

```{r}
# get data into long format
long_bib <- bibs %>% unnest_longer(col = AUTHOR)

@@

# drop editor column so it is a non-nested DF
long_bib <- long_bib %>% select(-EDITOR)
write.csv(long_bib, "unedited_bib.csv", row.names = F)
```

@@

write.csv(get_id, "possible_orc_ids.csv", row.names = F)
```

@@

```{r eval = F}
get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
{
    if (!any(nzchar(c(first_name, last_name)))) 
        stop("At least one of first and last name must be specified!")
    site <- getOption("scholar_site")
    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
        first_name, "+", last_name, "&hl=en&oi=ao")
    page <- get_scholar_resp(url)
    if (is.null(page)) 
        return(NA)
    aa <- content(page, as = "text")
    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')

@@

write.csv(get_id, "possible_both_ids.csv", row.names = F)
```

>>>>

```{r}
library(dplyr)
library(purrr)
library(bib2df)
library(tidyverse)
library(httr)
library(googlesheets4)

@@

library(scholar)
library(rio)
```

@@

```{r eval = F}
# bibs <- bib2df("papers.bib")
bibs <- bib2df("manuscript_data/papers_06_17_22.bib")
```

@@

```{r eval = F}
# get data into long format
long_bib <- bibs %>% unnest_longer(col = AUTHOR)

@@

# drop editor column so it is a non-nested DF
long_bib <- long_bib %>% select(-EDITOR)
write.csv(long_bib, "id_output/unedited_bib.csv", row.names = F)
```

@@

write.csv(get_id, "id_output/possible_orc_ids.csv", row.names = F)
```

@@

```{r}
get_scholar <- function (last_name = "", first_name = "", affiliation = NA) 
{
    if (!any(nzchar(c(first_name, last_name)))) 
        stop("At least one of first and last name must be specified!")
    site <- getOption("scholar_site")
    url <- paste0(site, "/citations?view_op=search_authors&mauthors=", 
        first_name, "+", last_name, "&hl=en&oi=ao")
    page <- get_scholar_resp(url)
    if (is.null(page)) 
        return(NA)
    aa <- content(page, as = "text")
    ids <- stringr::str_extract_all(string = aa, pattern = ';user=.{12}')

@@

write.csv(get_id, "id_output/possible_both_ids.csv", row.names = F)
```

## Get Data Round 2

```{r}
DF <- read_sheet("https://docs.google.com/spreadsheets/d/1dSlIQXeLcFgkITyfy15_yAdtjct1AedjD6s5D4qTzCw/edit#gid=1698777071")
```

## Work on ORC

```{r eval = F}
ORC <- DF %>% 
  filter(ORCID == "FIND")

for (i in 2447:nrow(ORC)){
#for (i in 1:10){ #temporary do a small number

  # find possible candidates 
  possibles <- orcid_search(family_name = ORC$last[i], 
                            given_name = ORC$first[i])

  # if nrow == 1 then figure out if there's a match
  if (nrow(possibles) == 1){
    ORC$ORCID[i] <- possibles$orcid
  }

DF <- DF %>% 
  full_join(ORCF %>% select(first, last, ORCID), 
            by = c("first" = "first", "last" = "last"))

export(DF, "id_output/orc_final.xlsx")
```

## Get Scholar IDs

```{r}
scholars <- DF %>% filter(scholar == "FIND")
p_get_scholar_id <- possibly(get_scholar, otherwise = NA_character_)

nrow(scholars)
# start at Bergmann 134

for(i in 258:300) {

  possibles <- p_get_scholar_id(last_name = scholars$last[i], 
                                first_name = scholars$first[i])

  if (length(possibles) == 1) { scholars$scholar[i] <- possibles }

  # be nice to api take a break 
  Sys.sleep(runif(5, 3, 5))

  # if divisible by 10
  if (i %% 10 == 0){
    export(scholars, "id_output/scholar_update.xlsx")
  }
}

DF <- DF %>% 
  full_join(scholars %>% select(first, last, scholar), 
            by = c("first" = "first", "last" = "last"))

export(DF, "id_output/scholar_final.xlsx")

```

### 2022-07-08 02.get_person_stats.Rmd
rearranging

write.csv(works_df, "ORCID_works.csv", row.names = F)

@@

write.csv(ed_df, "ORCID_ed.csv", row.names = F)

job_df <- do.call(bind_rows, author_job)
job_df$ORCID <- rep(names(author_job), lapply(author_job, nrow))
job_df <- job_df %>%
  dplyr::mutate(employment_summary_end_date =
                  anytime::anydate(employment_summary_end_date/1000),
                employment_summary_created_date_value =
                  anytime::anydate(employment_summary_created_date_value/1000),
                employment_summary_last_modified_date_value =
                  anytime::anydate(employment_summary_last_modified_date_value/1000))
write.csv(job_df, "ORCID_job.csv", row.names = F)
```

@@

works_df <- do.call(bind_rows, s_author_works) 
works_df$scholar <- rep(names(s_author_works), lapply(s_author_works, nrow))
write.csv(works_df, "scholar_works.csv", row.names = F)

@@

info_df <- do.call(bind_rows, s_author_info) 
info_df$scholar <- info_df$id
write.csv(info_df, "scholar_info.csv", row.names = F)
```

>>>>

write.csv(works_df, "works_output/ORCID_works.csv", row.names = F)

@@

write.csv(ed_df, "works_output/ORCID_ed.csv", row.names = F)

job_df <- do.call(bind_rows, author_job)
job_df$ORCID <- rep(names(author_job), lapply(author_job, nrow))
job_df <- job_df %>%
  dplyr::mutate(employment_summary_end_date =
                  anytime::anydate(employment_summary_end_date/1000),
                employment_summary_created_date_value =
                  anytime::anydate(employment_summary_created_date_value/1000),
                employment_summary_last_modified_date_value =
                  anytime::anydate(employment_summary_last_modified_date_value/1000))
write.csv(job_df, "works_output/ORCID_job.csv", row.names = F)
```

@@

works_df <- do.call(bind_rows, s_author_works) 
works_df$scholar <- rep(names(s_author_works), lapply(s_author_works, nrow))
write.csv(works_df, "works_output/scholar_works.csv", row.names = F)

@@

info_df <- do.call(bind_rows, s_author_info) 
info_df$scholar <- info_df$id
write.csv(info_df, "works_output/scholar_info.csv", row.names = F)
```

### 2022-07-08 03.data_analysis.Rmd
rearranging

```{r}
# bibs <- bib2df("papers.bib") original data
bibs <- bib2df("papers_06_17_22.bib")

@@

```{r}
id_list <- import("test_utf8.xlsx")

o_works <- import("ORCID_works.csv")
o_ed <- import("ORCID_ed.csv")
o_job <- import("ORCID_job.csv")

s_works <- import("scholar_works.csv") 
s_info <- import("scholar_info.csv")
```

@@

# if full name is blank, then the person is not in our id_list
merged_test %>% 
  filter(!duplicated(merged_test %>% select(first, last))) %>% 
  filter(is.na(full)) %>% 
  export("missing_id_list.xlsx")

# if no title they are in id_list but aren't merging correctly 
merged_test %>% 
  filter(is.na(TITLE)) %>% 
  export("incorrect_id_list.xlsx")
```

@@

```{r}
JIF <- import("jif.xlsx")
```

>>>>

```{r}
# bibs <- bib2df("papers.bib") original data
bibs <- bib2df("manuscript_data/papers_06_17_22.bib")

@@

```{r}
id_list <- import("manuscript_data/test_utf8.xlsx")

o_works <- import("works_output/ORCID_works.csv")
o_ed <- import("works_output/ORCID_ed.csv")
o_job <- import("works_output/ORCID_job.csv")

s_works <- import("works_output/scholar_works.csv") 
s_info <- import("works_output/scholar_info.csv")
```

@@

# if full name is blank, then the person is not in our id_list
merged_test %>% 
  filter(!duplicated(merged_test %>% select(first, last))) %>% 
  filter(is.na(full)) %>% 
  export("id_output/missing_id_list.xlsx")

# if no title they are in id_list but aren't merging correctly 
merged_test %>% 
  filter(is.na(TITLE)) %>% 
  export("id_output/incorrect_id_list.xlsx")
```

@@

```{r}
JIF <- import("manuscript_data/jif.xlsx")
```
